A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-08 mt-marathon.2013/PBML_article.tex
corrected statement about sentence markers in joshua

Given the same formalism and model data, the results from the decoders are comparable, after adjusting for scaling differences and constants. Figure~\ref{fig:model} shows the comparison of model scores and BLEU scores for a hierarchical model. Moses and cdec are roughly comparable in terms of speed. Also, Moses and cdec converges to roughly the same model scores, while Joshua makes more search errors. This is due to two issues that have been resolved in Moses and cdec, but not yet in Joshua.

@@

Firstly, in Moses and cdec, the calculation of language model state is delegated to the language model implementation~\cite{Heafield-left} which uses the internal data-structure of the language model to determine state (??? Ney paper from yrs ago). Joshua, on the other hand, uses the words in the left and right context to determine language model state. This results in more aggressive hypothesis recombination in Moses and cdec, leading to better model score.

Secondly, the glue rule formulation in Moses and cdec is different from Joshua's. In Moses and cdec, the glue rule grammar is:
\begin{verbatim}
   S -> <s>
   S -> S X
   GOAL -> S </s> 
\end{verbatim}
where <s> and </s> are first-class words like any other. In Joshua, the glue rule grammar is:
\begin{verbatim}
   S -> X
   S -> S X
   GOAL -> <s> S </s> 
\end{verbatim}
In the Moses and cdec formulation, glued hypotheses know that they are bound to the beginning of sentence <s>.  Therefore, their left language model state is empty and more hypotheses can recombine.  This is better than Joshua, where hypotheses are informed about <s> and </s> only after forming a complete sentence, so the left states are spuriously ambiguous.  Moreover, hypothesis score estimates are more accurate when they know about <s> earlier. Figure~\ref{fig:glue} shows the improvement in cdec by changing the glue rule formulation. This improvement was the direct result of research comparing the three decoders.

\begin{figure}[h]
\begin{center}
\input{1111-8/glue_model.tex}
\end{center}
\caption{Effect on model score by changing glue-rule formulation}
\label{fig:glue}
\end{figure}

>>>>

Given the same formalism and model data, the results from the decoders are comparable, after
adjusting for scaling differences and constants. Figure~\ref{fig:model} shows the comparison of
model scores and BLEU scores for a hierarchical model. Moses and cdec are roughly comparable in
terms of speed. Also, Moses and cdec converges to roughly the same model scores, while Joshua makes
more search errors.

@@

This is likely due to the fact that in Moses and cdec, the calculation of language model state is delegated to the language model implementation~\cite{Heafield-left} which uses the internal data-structure of the language model to determine state (??? Ney paper from yrs ago). Joshua, on the other hand, uses the words in the left and right context to determine language model state. This results in more aggressive hypothesis recombination in Moses and cdec, leading to better model score.

%% (2013-07-08 Matt Post): This isn't true; Joshua does include the <s> and </s> symbols and allows
%% early combination with <s> (this was implemented last summer). Model scores between Moses and
%% Joshua are exact, now, with a properly converted model. The main decoder difference seems to be
%% that Joshua does not incorporate lefthand-side LM state collapsing for OOVs. I've commented out
%% the below because I think you'll want to include it but it will have to be moved somewhere
%% outside the discussion of differences from Joshua.

%% Secondly, the glue rule formulation in Moses and cdec is different from Joshua's. In Moses and cdec, the glue rule grammar is:
%% \begin{verbatim}
%%    S -> <s>
%%    S -> S X
%%    GOAL -> S </s> 
%% \end{verbatim}
%% where <s> and </s> are first-class words like any other. In Joshua, the glue rule grammar is:
%% \begin{verbatim}
%%    S -> X
%%    S -> S X
%%    GOAL -> <s> S </s> 
%% \end{verbatim}
%% In Moses and cdec formulation, glued hypotheses know that they are bound to the beginning of sentence <s>.  Therefore, their left language model state is empty and more hypotheses can recombine.  This is better than Joshua, where hypotheses are informed about <s> and </s> only after forming a complete sentence, so the left states are spuriously ambiguous.  Moreover, hypothesis score estimates are more accurate when they know about <s> earlier. Figure~\ref{fig:glue} shows the improvement in cdec by changing the glue rule formulation. This improvement was the direct result of research comparing the three decoders.

%% \begin{figure}[h]
%% \begin{center}
%% \input{1111-8/glue_model.tex}
%% \end{center}
%% \caption{Affect on model score by changing glue-rule formulation}
%% \label{fig:glue}
%% \end{figure}
